Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Line numbers.

\usepackage{lineno}

@@

%% Title, authors and addresses
\title{Robust Bayesian Analysis of Causal Inference Problems}
\author[1]{Tathagata Basu\corref{cor1}}
\ead{tathagatabasumaths@gmail.com}
\cortext[cor1]{Corresponding author}
\author[2]{Matthias C.~M.~Troffaes}
\ead{matthias.troffaes@durham.ac.uk}
\affiliation[1]{organization={Civil and Environmental Engineering, University of Strathclyde},
            addressline={}, 
            city={},
            postcode={}, 
            state={},
            country={}}
\affiliation[2]{organization={Department of Mathematical Sciences, Durham University},
            addressline={South Road}, 
            city={Durham},
            postcode={DH13LE}, 
            state={},
            country={United Kingdom}}

>>>>

\usepackage{lineno}
\linenumbers

@@

%% Title, authors and addresses
\title{Robust Bayesian Analysis of Causal Inference Problems}
\author[1]{Tathagata Basu\corref{cor1}}
\ead{tathagatabasumaths@gmail.com}
\cortext[cor1]{Corresponding author}
\author[2]{Matthias C.~M.~Troffaes}
\ead{matthias.troffaes@durham.ac.uk}
\affiliation[1]{organization={Civil and Environmental Engineering, University of Strathclyde},
            addressline={}, 
            city={},
            postcode={}, 
            state={},
            country={}}
\affiliation[2]{organization={Department of Mathematical Sciences, Durham University},
            addressline={South Road}, 
            city={Durham},
            postcode={DH13LE}, 
            %state={},
            country={United Kingdom}}
